Viscous Transport in Eroding Porous Media

### 2019-06-11 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
if the difference of length of the neighboring trajectories is large. From this figure, we are able to 
tell the neighboring trajectories will be very different if they are separated by bodies. 
}

>>>>

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
if the difference of length of the neighboring trajectories is large. From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
The pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}
